### 2009-08-06 papers/SBMF2009/Presentation/content/3_Modelling.tex
The presentation

\section{Modelling the Instruction Set in B}
\begin{frame}
  \frametitle{Modelling  Microcontrollers}

  \begin{itemize}[<+->]
  \item Relations 
  \begin{itemize}
  	\item States of platform  $\Leftrightarrow$ States of modell
		\begin{itemize}
		\item Registers and Memory $\Leftrightarrow$  Variables of model
		\end{itemize}
	\item Assembly Instructions $\Leftrightarrow$ B operations
        \begin{itemize}
        \item Changes of states of platform $\Leftrightarrow$ B substitutions
        \end{itemize}
  \end{itemize}

 \end{itemize}
\end{frame}

\begin{frame}
 \frametitle{Structure of Projects B}
 \begin{center}\includegraphics[width=1.\textwidth]{figures/diagramaEstrutural_vertical.png}
 \end{center}

@@

\begin{frame}
 \frametitle{Project Hardware Library}

@@

\begin{frame}
 \frametitle{Projeto \textit{Hardware Library}}

@@

           \item The module \textit{BIT\_VECTOR\_ARITHMETICS} define basics arithmetic functions
           \item The module \textit{BYTE} e \textit{BV16\_DEFINITION} define specialized functions to bit vectors of size 8 and 16
 	\end{itemize}

@@

\begin{frame}
 \frametitle{Platform project(Z80)}
  \begin{itemize}
    \item Z80 is a microcontroller  of 8 bits with addressing of 16 bits
    \item Supports:
    \begin{itemize}
      \item 158 instructions (included all of 8080 microcontroller )
      \item Several addressing modes and interruption types
      \item 256 input and output ports (8 bits)
      \item Some operations with 16 bits
    \end{itemize}

      \item Header of modelling B
  \end{itemize}

	 {\scriptsize
	 \begin{sloppypar}
	\hspace*{1.0in}\bf MACHINE\\
	\hspace*{1.15in}\it Z80\\
	\hspace*{1.0in}\bf INCLUDES\\
	\hspace*{1.10in}\it MEMORY\\
	\hspace*{1.0in}\bf SEES\\
	\hspace*{1.10in}\it ALU, \it BIT\_DEFINITION, \it BIT\_VECTOR\_DEFINITION,\\
	\hspace*{1.10in}\it BYTE\_DEFINITION, \it BV16\_DEFINITION,\\
	\hspace*{1.10in}\it UCHAR\_DEFINITION, \it SCHAR\_DEFINITION,\\
	\hspace*{1.10in}\it SSHORT\_DEFINITION ,\it USHORT\_DEFINITION\\
	\end{sloppypar}
	}

@@

\begin{frame}
\frametitle{Modelling Registers, input/output ports and instructions from Z80}

 \begin{itemize}
   \item The invariant:

	{\scriptsize
	\begin{sloppypar}
	%\bf INVARIANT\\
	\hspace*{0.10in}\it rgs8  $\in$  \it id\_reg\_8  $\fun$  \it BYTE  $\land$ pc  $\in$  \it INSTRUCTION
	$\land$\\
	\hspace*{0.10in}\it  sp  $\in$  \it BV16  $\land$  \it ix  $\in$  \it BV16  $\land$  \it iy  $\in$  \it
	BV16  $\land$\\
	\hspace*{0.10in}\it i\_  $\in$  \it BYTE  $\land$  \it r\_ $\in$  \it BYTE  $\land$ iff1  $\in$  \it BIT
	$\land$ \it iff2  $\in$  \it BIT  $\land$ \\
	\hspace*{0.10in}\it im \rm $\in$ \rm (\it BIT $\times$ \it BIT\rm )  $\land$ \it i\_o\_ports  $\in$
	\it BYTE $\fun$  \it BYTE\\
	\end{sloppypar}
	}
	\item A simple instruction
	{\scriptsize
	\begin{sloppypar}
	\hspace*{0.10in}\bf LD\_n\_A \rm ( \it nn \rm ) \rm =\\
	\hspace*{0.20in}\bf PRE \it nn $\in$ \it USHORT\hspace*{0.15in}\\ %$\land$  \it nn $\in$\it DATA\_R\_ADR
	\hspace*{0.20in}\bf THEN\\
	\hspace*{0.20in}\bf updateAddressMem \rm ( \it ushort\_to\_bv16 \rm ( \it nn \rm ) \rm , \it rgs8 \rm ( \it a0 \rm )
	\rm )  $\para$\\
	\hspace*{0.20in}\it pc \rm := \it instruction\_next \rm ( \it pc \rm )  $\para$  \it r\_ \rm := \it
	update\_refresh\_reg\rm (\it r\_\rm )\\
	\hspace*{0.10in}\bf END\rm
	\end{sloppypar}

@@

	\end{itemize}
% \end{itemize}
% 	\begin{center}
% 	{\small
% 	$$
% 	\begin{array}{l}
% 	\mathit{BTFSS} (\mathit{ff}, \mathit{bb}) =\\
% 	\quad \PRE \mathit{ff} : \mathit{REGISTER} \land  \mathit{bb} : \mathit{BYTE\_INDEX} \\
% 	\quad \THEN \\
% 	\quad \quad	\IF \mathit{bitget}(\mathit{mem}(\mathit{ff}), \mathit{bb}) = 1 \THEN\\
% 	\quad\quad\quad	   \mathit{pc} :=\mathit{instruction\_next}(\mathit{instruction\_next}(\mathit{pc}))\\
% 	\quad\quad	\ELSE\\
% 	\quad\quad\quad	  \mathit{pc} := \mathit{instruction\_next}(\mathit{pc})\\
% 	\quad\quad	\END\\
% 	\quad \END
% 	\end{array}
% 	$$
% 	}\\
% 	Instrução de controle do \textit{PIC16C432}
%
% 	\end{center}

>>>>

\section{Modelling the Instruction Set in B}
% \begin{frame}
%   \frametitle{Modelling  Microcontrollers}  
% 
%   \begin{itemize}[<+->]
%   \item Relations 
%   \begin{itemize}
%   	\item States of platform  $\Leftrightarrow$ States of modell
% 		\begin{itemize}
% 		\item Registers and Memory $\Leftrightarrow$  Variables of model
% 		\end{itemize}
% 	\item Assembly Instructions $\Leftrightarrow$ B operations
%         \begin{itemize}
%         \item Changes of states of platform $\Leftrightarrow$ B substitutions
%         \end{itemize}
%   \end{itemize}
%     
%  \end{itemize}
% \end{frame}

\begin{frame}
 \frametitle{Structure of B Projects}
 \begin{center}\includegraphics[width=1.\textwidth]{figures/diagramaEstrutural_vertical.png}
 \end{center}

@@

\begin{frame}
 \frametitle{Hardware Library Project}

@@

\begin{frame}
 \frametitle{Hardware Library Project}

@@

           \item The module \textit{BIT\_VECTOR\_ARITHMETICS} define basics arithmetic functions
           \item The module \textit{BYTE} and \textit{BV16\_DEFINITION} define specialized functions to
           bit vectors of size 8 and 16
 	\end{itemize}

@@

\begin{frame}
 \frametitle{Platform Project(Z80)}
  \begin{itemize}
    \item Z80 is a microcontroller  of 8 bits with addressing of 16 bits
    \item Supports:
    \begin{itemize}
      \item 158 instructions (included all of 8080 microcontroller )
      \item Several addressing modes and interruption types
      \item 256 input and output ports (8 bits)
      \item Some operations with 16 bits
    \end{itemize}

  \item Modelling 
  \begin{itemize}
  	\item States of platform  $\Leftrightarrow$ States of modell
		\begin{itemize}
		\item Registers and Memory $\Leftrightarrow$  Variables of model
		\end{itemize}
	\item Assembly Instructions $\Leftrightarrow$ B operations
        \begin{itemize}
        \item Changes of states of platform $\Leftrightarrow$ B substitutions
        \end{itemize}

@@

\begin{frame}
\frametitle{Modelling Registers, Input/Output Ports and Instructions from Z80}
%  \begin{itemize}
%  \item Header of Modelling B
%  \end{itemize}  
	 {\scriptsize
	 \begin{sloppypar}
		\hspace*{.0in}\bf MACHINE\\
		\hspace*{.15in}\it Z80\\
		\hspace*{.0in}\bf INCLUDES\\
		\hspace*{.10in}\it MEMORY\\
		\hspace*{.0in}\bf SEES\\ \ldots
	% 	\hspace*{1.10in}\it ALU, \it BIT\_DEFINITION, \it BIT\_VECTOR\_DEFINITION,\\
	% 	\hspace*{1.10in}\it BYTE\_DEFINITION, \it BV16\_DEFINITION,\\
	% 	\hspace*{1.10in}\it UCHAR\_DEFINITION, \it SCHAR\_DEFINITION,\\
	% 	\hspace*{1.10in}\it SSHORT\_DEFINITION ,\it USHORT\_DEFINITION\\
		\end{sloppypar}
	}
% \begin{itemize}  
 %  \item The invariant:

	{\scriptsize
	\begin{sloppypar}
	\bf INVARIANT\\
	\hspace*{0.10in}\it rgs8  $\in$  \it id\_reg\_8  $\fun$  \it BYTE  $\land$ pc  $\in$  \it INSTRUCTION
	$\land$\\
	\hspace*{0.10in}\it  sp  $\in$  \it BV16  $\land$  \it ix  $\in$  \it BV16  $\land$  \it iy  $\in$  \it
	BV16  $\land$\\
	\hspace*{0.10in}\it i\_  $\in$  \it BYTE  $\land$  \it r\_ $\in$  \it BYTE  $\land$ iff1  $\in$  \it BIT
	$\land$ \it iff2  $\in$  \it BIT  $\land$ \\
	\hspace*{0.10in}\it im \rm $\in$ \rm (\it BIT $\times$ \it BIT\rm )  $\land$ \it i\_o\_ports  $\in$
	\it BYTE $\fun$  \it BYTE\\
	\ldots
	\end{sloppypar}

@@

%	\item A simple instruction
	{\scriptsize
	\begin{sloppypar}
    \bf OPERATIONS\\
	\hspace*{0.10in}\bf LD\_n\_A \rm ( \it nn \rm ) \rm =\\
	\hspace*{0.20in}\bf PRE \it nn $\in$ \it USHORT\hspace*{0.15in}\\ %$\land$  \it nn $\in$\it DATA\_R\_ADR
	\hspace*{0.20in}\bf THEN\\
	\hspace*{0.20in}\bf updateAddressMem \rm ( \it ushort\_to\_bv16 \rm ( \it nn \rm ) \rm , \it rgs8 \rm ( \it a0 \rm )
	\rm )  $\para$\\
	\hspace*{0.20in}\it pc \rm := \it instruction\_next \rm ( \it pc \rm )  $\para$  \it r\_ \rm := \it
	update\_refresh\_reg\rm (\it r\_\rm )\\
	\hspace*{0.10in}\bf END\rm
	\ldots
	\end{sloppypar}

	%\end{itemize}
% \end{itemize}
% 	\begin{center}
% 	{\small
% 	$$
% 	\begin{array}{l}
% 	\mathit{BTFSS} (\mathit{ff}, \mathit{bb}) =\\
% 	\quad \PRE \mathit{ff} : \mathit{REGISTER} \land  \mathit{bb} : \mathit{BYTE\_INDEX} \\
% 	\quad \THEN \\
% 	\quad \quad	\IF \mathit{bitget}(\mathit{mem}(\mathit{ff}), \mathit{bb}) = 1 \THEN\\
% 	\quad\quad\quad	   \mathit{pc} :=\mathit{instruction\_next}(\mathit{instruction\_next}(\mathit{pc}))\\
% 	\quad\quad	\ELSE\\
% 	\quad\quad\quad	  \mathit{pc} := \mathit{instruction\_next}(\mathit{pc})\\
% 	\quad\quad	\END\\
% 	\quad \END
% 	\end{array}
% 	$$
% 	}\\
% 	Instrução de controle do \textit{PIC16C432}
%
% 	\end{center}
